B\'{e}zier $\bar{B}$ projection

### 2018-01-24 projection1120.tex
remark added

Localizing to the B\'{e}zier element we define the strain-displacement arrays in terms of element Bernstein basis functions of degree $p$ and $p-1$ as
\begin{align}
	\mathbf{B}_e^\kappa 
    	&= \begin{bmatrix} 0 & -{B^e_{0,p}}' & \cdots & 0 & -{B^e_{p,p}}' \end{bmatrix}, \\
    \mathbf{B}_e^\gamma
    	&= \begin{bmatrix} {B^e_{0,p}}' & -B^e_{0,p} & \cdots & {B^e_{p,p}}' & -B^e_{p,p} \end{bmatrix}, \\
    \bar{\mathbf{B}}_e
    	&= \begin{bmatrix} \bar{B}^e_{0,p-1} & \cdots & \bar{B}^e_{p-1,p-1} \end{bmatrix},
\end{align}
\added{where $B^e_{i,p}$ is the $i^{th}$ Bernstein basis function of order $p$}. We can then compute the element arrays as
\begin{align}
\mathbf{K}_e^b &= EI\mathbf{C}^e\langle{{\mathbf{B}_e^\kappa}^T,\mathbf{B}_e^\kappa}\rangle(\mathbf{C}^e)^T, \label{eq:symmetric_timoshenko}\\
\bar{\mathbf{M}}_e &= s{GA}\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\bar{\mathbf{B}}_e}\rangle(\bar{\mathbf{C}}^e)^T, \\
\replaced{\hat{\mathbf{P}}_e}{\mathbf{P}_e} &= \langle{(\hat{\bar{\mathbf{N}}}^e)^T,\mathbf{B}^\gamma_e}\rangle(\mathbf{C}^e)^T,
\end{align}
where $\mathbf{C}^e$ is the element extraction operator for the degree $p$ spline space, $\bar{\mathbf{C}}^e$ is the element extraction operator for the degree $p-1$ spline space, and $\hat{\bar{\mathbf{N}}}^e$ are the dual basis functions restricted to the element for the degree $p-1$ spline space. The global stiffness matrix can then be written as
\begin{align}
	\mathbf{K} = \mathbf{K}^b + \bar{\mathbf{K}}^s_S
\end{align}
where
\begin{align}
	\mathbf{K}^b &=\A_e\mathbf{K}_e^b,\label{eqn:bending_stiffness} \\
	\bar{\mathbf{K}}^s&=\replaced{\hat{\mathbf{P}}}{\mathbf{P}}^T\bar{\mathbf{M}}\replaced{\hat{\mathbf{P}}}{\mathbf{P}}\label{eqn:shear_stiffness} \\
	\replaced{\hat{\mathbf{P}}}{\mathbf{P}} &=\A_e\replaced{\hat{\mathbf{P}}_e}{\mathbf{P}_e} \\
    \bar{\mathbf{M}} &=\A_e\bar{\mathbf{M}}_e
\end{align}
and $\A$ is the standard finite element assembly operator \cite{hughes_finite_2012}. We note that the assembly of $\bar{\mathbf{K}}^s$ requires the assembly of two intermediate matrices, $\bar{\mathbf{M}}$ and $\replaced{\hat{\mathbf{P}}}{\mathbf{P}}$. The computation of these matrices is needed because the product of two integrals over the entire domain can not be localized to the element level.
\subsection{Non-symmetric \Bezier $\bar{B}$ projection}
\label{sec:non-symmetric}

@@

\paragraph{Remark}

@@

âˆ

@@

\mathbf{B}^{dev}_e&=

@@

\mathbf{B}_e^{vol}&=

>>>>

Localizing to the B\'{e}zier element we define the strain-displacement arrays in terms of element Bernstein basis functions of degree $p$ and $p-1$ as
\begin{align}
	\mathbf{B}_e^\kappa 
    	&= \begin{bmatrix} 0 & -{B^e_{0,p}}' & \cdots & 0 & -{B^e_{p,p}}' \end{bmatrix}, \\
    \mathbf{B}_e^\gamma
    	&= \begin{bmatrix} {B^e_{0,p}}' & -B^e_{0,p} & \cdots & {B^e_{p,p}}' & -B^e_{p,p} \end{bmatrix}, \\
    \bar{\mathbf{B}}_e
    	&= \begin{bmatrix} \bar{B}^e_{0,p-1} & \cdots & \bar{B}^e_{p-1,p-1} \end{bmatrix},
\end{align}
\added{where $B^e_{i,p}$ is the $i^{th}$ Bernstein basis function of order $p$}. We can then compute the element arrays as
\begin{align}
\mathbf{K}_e^b &= EI\mathbf{C}^e\langle{{\mathbf{B}_e^\kappa}^T,\mathbf{B}_e^\kappa}\rangle(\mathbf{C}^e)^T, \label{eq:symmetric_timoshenko}\\
\bar{\mathbf{M}}_e &= s{GA}\bar{\mathbf{C}}^e\langle{\bar{\mathbf{B}}_e^T,\bar{\mathbf{B}}_e}\rangle(\bar{\mathbf{C}}^e)^T, \\
\replaced{\hat{\mathbf{P}}_e}{\mathbf{P}_e} &= \langle{(\hat{\bar{\mathbf{N}}}^e)^T,\mathbf{B}^\gamma_e}\rangle(\mathbf{C}^e)^T,
\end{align}
where $\mathbf{C}^e$ is the element extraction operator for the degree $p$ spline space, $\bar{\mathbf{C}}^e$ is the element extraction operator for the degree $p-1$ spline space, and $\hat{\bar{\mathbf{N}}}^e$ are the dual basis functions restricted to the element for the degree $p-1$ spline space. The global stiffness matrix can then be written as
\begin{align}
	\mathbf{K} = \mathbf{K}^b + \bar{\mathbf{K}}^s_S \label{eqn:symmetric_b_bar_timoshenko_stiffness}
\end{align}
where
\begin{align}
	\mathbf{K}^b &=\A_e\mathbf{K}_e^b,\label{eqn:bending_stiffness} \\
	\bar{\mathbf{K}}^s&=\replaced{\hat{\mathbf{P}}}{\mathbf{P}}^T\bar{\mathbf{M}}\replaced{\hat{\mathbf{P}}}{\mathbf{P}}\label{eqn:shear_stiffness} \\
	\replaced{\hat{\mathbf{P}}}{\mathbf{P}} &=\A_e\replaced{\hat{\mathbf{P}}_e}{\mathbf{P}_e} \\
    \bar{\mathbf{M}} &=\A_e\bar{\mathbf{M}}_e
\end{align}
and $\A$ is the standard finite element assembly operator \cite{hughes_finite_2012}. We note that the assembly of $\bar{\mathbf{K}}^s$ requires the assembly of two intermediate matrices, $\bar{\mathbf{M}}$ and $\replaced{\hat{\mathbf{P}}}{\mathbf{P}}$. The computation of these matrices is needed because the product of two integrals over the entire domain can not be localized to the element level.
\subsection{Non-symmetric \Bezier $\bar{B}$ projection}
\label{sec:non-symmetric}

@@

\paragraph{Remark} \added{From the stiffness matrix of the symmetric \Bezier $\bar{B}$ formulation \eqref{eqn:symmetric_b_bar_timoshenko_stiffness}, we can recover its mixed formulation as}

\begin{equation}
    \begin{bmatrix}
        \mathbf{K}^b & \hat{\mathbf{P}}^T \\
        sGA\hat{\mathbf{P}} & -\bar{\mathbf{M}}^{-1}
    \end{bmatrix},
\end{equation}
\added{where both the shear stress and its variation are discretized by the dual basis functions. However, for the inner product of dual basis functions }
\begin{equation}
    \langle{\hat{\bar{N}}_i,\hat{\bar{N}}_j}\rangle\neq{\bar{\mathbf{M}}^{-1}_{ij}},
\end{equation}
\added{which shows the conflict between the symmetric \Bezier $\bar{B}$ formulation and the mixed formulation.}

@@

∏

@@

\added{\mathbf{B}^{dev}_e}&=

@@

\added{\mathbf{B}_e^{vol}}&=
